A Large-Scale Study of Polymorphism in R

### 2019-04-05 paper/main.tex
automatic subtying discussion

>>>>

\subsection{Automatic Subtyping}
\label{sec:autosub}

When analyzing our data, we perform a certain amount of subtyping automatically to minimize the footprint of obviously equivalent signatures.
This subtyping is performed at the function level of granularity.
For example, if a function is observed to have two signatures \sD \to \df to \D \to \df, we collapse the signature to \D \to \df as \sD $<:$ \D and \df $<:$ \df.
We would not collapse \sD, \I \to \df and \D, \sI \to \df, as \I $\not <:$ \sI and \D $\not<:$ \sD.
